### 2020-04-07 submission/manuscript.tex
Incorporate edits from AKH, KLS, BT, and PDS

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1.0in]{geometry}
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font

@@

\vspace{10mm}

\section{Ten Simple Rules to increase computational skills among
biologists with Code
Clubs}\label{ten-simple-rules-to-increase-computational-skills-among-biologists-with-code-clubs}

Ada K. Hagan\({^2}\), Nick Lesniak, \emph{Author names here, order TBD}

Patrick D. Schloss\({^1}\)\({^\dagger}\)

@@

\subsubsection{Ten Simple Rules}\label{ten-simple-rules}

\linenumbers

\subsection{Introduction}\label{introduction}

@@

We continue to experiment with approaches to running Code Club, but have
learned that it is critical for the presenter to clearly articulate
their goals and facilitate participant engagement. Although any
individual Code Club session may be more experimental than another, on
the whole they are a critical tool to train bench scientists in
reproducible data analysis practices. We have provided some examples of
successful code club topics in Table 1 and summarized the results of our
own experimentation as Code Club presenters and participants into Ten
Rules. The first 3 rules apply to all participants at every Code Club,
while Rules 4 through 8 are targeted to Code Club presenters and the
last two for participants.

\subsection{Rule 1: Reciprocate
respect}\label{rule-1-reciprocate-respect}

It is critical that the presenter and participants respect each other
and that a designated individual (e.g.~the lab director) enforces a code
of conduct (see X for an example). Each member of the Code Club must
have the humility to acknowledge that they have more to learn about any
given topic. We have found that many problems are avoided when the
presenter takes charge of the session with a clear lesson plan,
thoughtful group creation, and constructive encouragement. Similarly,
participants foster a positive environment by remembering that the task
is not a competition, focusing on the presenter's goals, allowing their
partner to contribute, asking clarifying questions when appropriate, and
avoiding distractions (e.g.~email, social media). Learning to program is
challenging and too often results in a toxic environment of nitpicking
and nonconstructive criticism. All parties in a Code Club are
responsible for preventing this toxicity by demonstrating respect for
themselves and their colleagues.

\subsection{Rule 2: Let the material change
you}\label{rule-2-let-the-material-change-you}

Part of the humility required to participate in a Code Club is
acknowledging that your training is incomplete and that it is possible
for you to learn something new. For participants, assume that the
presenter has a plan and follow their presented approach. After the Code
Club, try to incorporate that material into new code or refactor old
code. By practicing the material in a different context you will learn
the material better. For presenters, incorporate suggested changes into
your code. Either party may identify concepts that they are unsure of,
presenting opportunities for further conversation and learning.

\subsection{Rule 3: Experiment!}\label{rule-3-experiment}

@@

\subsection{Rule 4: Set specific goals}\label{rule-4-set-specific-goals}

@@

\subsection{Rule 5: Keep it simple}\label{rule-5-keep-it-simple}

@@

\subsection{Rule 6: Give participants time to
prepare}\label{rule-6-give-participants-time-to-prepare}

@@

\subsection{Rule 7: Don't give participants busy
work}\label{rule-7-dont-give-participants-busy-work}

@@

\subsection{Rule 8: Include all levels of
participants}\label{rule-8-include-all-levels-of-participants}

As suggested by Rule 7, a significant challenge to presenting at Code
Club is selecting topics and activities that appeal to a critical mass
of the participants. This is particularly difficult if participants have
a wide range of coding experience, such as follows a turnover in group
membership. In these circumstances it can be useful to cover commonly
used tools but that might result in disinterest of more experienced
participants. We have identified several strategies to overcome the
challenges presented by participants at varying skill levels. Instead of
letting participants form their own pairs, the presenter can select
pairs of participants with either similar or differing skill levels,
depending on their goals. Partnerships between those with similar skill
levels requires the presenter to design appropriate activites each skill
level. We have found that commenting code is a good skill for beginners
since it forces them to dissect and understand a code chunk
line-by-line. An advantage of partnerships with disparate skill levels
is assigning a single task, which provides the presenter with a diverse
range of methods that achieve the same result. This approach to pairing
also helps to graft new members into the group that have emerging
programming skills. Regardless of how partners are selected, consider
asking the pairs to identify a navigator and a driver {[}5{]}. The
driver types at the computer while the navigator tells them what to
type, thus ensuring participation of both partners. Midway through the
activity, the presenter can have the partners switch roles.
Intentionally forming pairs can also engineer group interactions by
breaking up cliques, avoiding potentially disruptive partnerships, or
pairing reliable role models with new group members.

\subsection{Rule 9: Prepare in advance to maximize
participation}\label{rule-9-prepare-in-advance-to-maximize-participation}

It is not possible to fully participate in a Journal Club discussion
about a paper that the participant has not read. In that context, coming
to Code Club without having installed a dependency is similar to asking
a simple question about the Journal Club paper. Both instances show a
lack of respect and preparation. Just as a presenter must follow Rule 6
to provide materials ahead of time, participants must review the code in
advance, download the data sets, install the necessary packages, and
perhaps read up on the topic. If the Code Club is based on a paper or
chapters in a data science book (e.g., {[}6--8{]}) the participants
should read them before the session and consider how they might
incorporate the concepts into their own work.

\subsection{Rule 10: Participate}\label{rule-10-participate}

An essential ingredient of any Code Club is active participation from
all parties. Having an open laptop on the table and permission to use it
can feel like an invitation to get distracted by other work, emails, and
browsing the internet; fight that urge and focus on the presenter's
goals. Be respectful and allow your partner to contribute. Speak up for
yourself and force your partner to let you contribute. If the material
seems too advanced for you, it can be frustrating, and tempting to
mentally check out. Fortuntately, programming languages like R and
Python are generally expressive, which should allow you to engage with
the logic, even if the syntax is too advanced. Frankly, understanding
the logic of when to use one modeling approach over another is more
important than how to use it. If you understand the ``why'', the ``how''
will quickly follow. More experienced participants should aim to
communicate feedback and coding suggestions at a level that all
participants can understand and engage in. Regardless of skill levels,
your partner and the presenter put themselves at risk by revealing what
they do or do not know. Encourage them, and show your gratitude for
helping you learn something new, by fully participating in each Code
Club.

\subsection{Conclusion}\label{conclusion}

@@

\subsection{Acknowledgements}\label{acknowledgements}

All co-authors have been participants in the Code Clubs run as part of
PDS's lab meetings. They have had a critical role in shaping the
evolution of the sessions. AKH led a lab discussion of Code Clubs to
identify the key concepts presented, which were supplemented by
contributions from NL. The order of co-authors was determined by\ldots{}

@@

\subsection{References}\label{references}

\hypertarget{refs}{}
\hypertarget{ref-Lonsdale2016}{}
1. Lonsdale A, Penington JS, Rice T, Walker M, Dashnow H. Ten simple
rules for a bioinformatics journal club. Lewitter F, editor. PLOS
Computational Biology. 2016;12: e1004526.
doi:\href{https://doi.org/10.1371/journal.pcbi.1004526}{10.1371/journal.pcbi.1004526}

\hypertarget{ref-Wilson2014}{}
2. Wilson G, Aruliah DA, Brown CT, Hong NPC, Davis M, Guy RT, et al.
Best practices for scientific computing. Eisen JA, editor. PLoS Biology.
2014;12: e1001745.
doi:\href{https://doi.org/10.1371/journal.pbio.1001745}{10.1371/journal.pbio.1001745}

\hypertarget{ref-Kothiyal2014}{}
3. Kothiyal A, Murthy S, Iyer S. Think-pair-share in a large CS1 class.
Proceedings of the 2014 conference on innovation \& technology in
computer science education - ITiCSE 14. ACM Press; 2014.
doi:\href{https://doi.org/10.1145/2591708.2591739}{10.1145/2591708.2591739}

\hypertarget{ref-StackOverflow_MREE}{}
4. Stack Overflow. How to create a minimal, reproducible example. 2020.
Available:
\url{https://stackoverflow.com/help/minimal-reproducible-example}

\hypertarget{ref-Bockeler_2020}{}
5. Böckeler B, Siessegger N. On pair programming. 2020. Available:
\url{https://martinfowler.com/articles/on-pair-programming.html}

\hypertarget{ref-Wickham_2016}{}
6. Wickham H, Grolemund G. O'Reilly Media; 2016. Available:
\url{https://r4ds.had.co.nz}

\hypertarget{ref-Schloss_2018}{}
7. Schloss PD. The riffomonas reproducible research tutorial series.
Journal of Open Source Education. 2018;1: 13.
doi:\href{https://doi.org/10.21105/jose.00013}{10.21105/jose.00013}

\hypertarget{ref-Noble2009}{}
8. Noble WS. A quick guide to organizing computational biology projects.
Lewitter F, editor. PLoS Computational Biology. 2009;5: e1000424.
doi:\href{https://doi.org/10.1371/journal.pcbi.1000424}{10.1371/journal.pcbi.1000424}

@@

\begin{longtable}[]{@{}ll@{}}
\toprule
\begin{minipage}[b]{0.24\columnwidth}\raggedright\strut
\textbf{Title}\strut
\end{minipage} & \begin{minipage}[b]{0.61\columnwidth}\raggedright\strut
\textbf{Description}\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
base vs.~ggplot\strut
\end{minipage} & \begin{minipage}[t]{0.61\columnwidth}\raggedright\strut
Given input data and a figure, recreate the figure using R's base
graphics or ggplot syntax\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
Snakemake\strut
\end{minipage} & \begin{minipage}[t]{0.61\columnwidth}\raggedright\strut
Given a bash script that contains an analysis pipeline, convert it to a
series of recipes (can also be done with GNU Make)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
DRYing code\strut
\end{minipage} & \begin{minipage}[t]{0.61\columnwidth}\raggedright\strut
Given script with repeated code, create functions to remove
repetition\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
mothur and Vegan\strut
\end{minipage} & \begin{minipage}[t]{0.61\columnwidth}\raggedright\strut
Given a pairwise community dissimilarity matrix, compare communities
using the \texttt{adonis} function in the Vegan R package\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
tidy data\strut
\end{minipage} & \begin{minipage}[t]{0.61\columnwidth}\raggedright\strut
Given a wide-formatted data table, convert it to a long, tidy-formatted
data table using tools from R's tidyverse\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
GitFlow\strut
\end{minipage} & \begin{minipage}[t]{0.61\columnwidth}\raggedright\strut
Participants file and claim an issue to add their name to a README file
in a GitHub-hosted repository and file a pull request to complete the
issue\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
Integrating R and Google docs\strut
\end{minipage} & \begin{minipage}[t]{0.61\columnwidth}\raggedright\strut
Scrape a Google docs workbook and clean the data to identify previous
Code Club presenters\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  11pt,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1.0in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font

@@

\vspace*{5mm}

\hypertarget{ten-simple-rules-to-increase-computational-skills-among-biologists-with-code-clubs}{%
\section{Ten Simple Rules to increase computational skills among
biologists with Code
Clubs}\label{ten-simple-rules-to-increase-computational-skills-among-biologists-with-code-clubs}}

\vspace{25mm}

Ada K. Hagan\({^2}\), Nick Lesniak, \emph{Author names here, order
alphabetical}, Patrick D. Schloss\({^1}\)\({^\dagger}\)

@@

\hypertarget{ten-simple-rules}{%
\subsubsection{Ten Simple Rules}\label{ten-simple-rules}}

\newpage
\linenumbers

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

@@

We continue to experiment with approaches to running Code Club. During
the period of the Covid-19 pandemic in 2020 when many research labs were
shuttered, PDS started hosting weekly Code Club virtually. Participants
could engage the material posted to
\url{https://www.riffomonas.org/code_club/} via a Zoom meeting or
asynchronously using the recorded sessions available on YouTube.
Regardless of our approach to leading a Code Club, we have learned that
it is critical for the presenter to clearly articulate their goals and
facilitate participant engagement. Although any individual Code Club
session may be more experimental than another, on the whole they are a
critical tool to train bench scientists in reproducible data analysis
practices. We have provided some examples of successful code club topics
in Table 1. We have summarized the results of our own experimentation as
Code Club presenters and participants into Ten Rules. The first 3 rules
apply to all participants at every Code Club, while Rules 4 through 8
are targeted to Code Club presenters and the last two for participants.

\hypertarget{rule-1-reciprocate-respect}{%
\subsection{Rule 1: Reciprocate
respect}\label{rule-1-reciprocate-respect}}

It is critical that the presenter and participants respect each other
and that a designated individual (e.g.~the lab director) enforces a code
of conduct (see X for an example). Each member of the Code Club must
have the humility to acknowledge that they have more to learn about any
given topic. We have found that many problems are avoided when the
presenter takes charge of the session with a clear lesson plan,
thoughtfully creating groups, and giving encouragement. Similarly,
participants foster a positive environment by remembering that the task
is not a competition, focusing on the presenter's goals, allowing their
partner to contribute, asking clarifying questions when appropriate, and
avoiding distractions (e.g.~email, social media). Learning to program is
challenging and too often results in a toxic environment of nitpicking
and nonconstructive criticism. All parties in a Code Club are
responsible for preventing this toxicity by demonstrating respect for
themselves and their colleagues.

\hypertarget{rule-2-let-the-material-change-you}{%
\subsection{Rule 2: Let the material change
you}\label{rule-2-let-the-material-change-you}}

Part of the humility required to participate in a Code Club is
acknowledging that your training is incomplete and that it is possible
for you to learn something new. For participants, assume that the
presenter has a plan and follow their presented approach. After the Code
Club, try to incorporate that material into new code or refactor old
code. By practicing the material in a different context, you will learn
the material better. For presenters, incorporate suggested changes into
your code. Either party may identify concepts that they are unsure of,
presenting opportunities for further conversation and learning.

\hypertarget{rule-3-experiment}{%
\subsection{Rule 3: Experiment!}\label{rule-3-experiment}}

@@

\hypertarget{rule-4-set-specific-goals}{%
\subsection{Rule 4: Set specific
goals}\label{rule-4-set-specific-goals}}

@@

\hypertarget{rule-5-keep-it-simple}{%
\subsection{Rule 5: Keep it simple}\label{rule-5-keep-it-simple}}

@@

\hypertarget{rule-6-give-participants-time-to-prepare}{%
\subsection{Rule 6: Give participants time to
prepare}\label{rule-6-give-participants-time-to-prepare}}

@@

\hypertarget{rule-7-dont-give-participants-busy-work}{%
\subsection{Rule 7: Don't give participants busy
work}\label{rule-7-dont-give-participants-busy-work}}

@@

\hypertarget{rule-8-include-all-levels-of-participants}{%
\subsection{Rule 8: Include all levels of
participants}\label{rule-8-include-all-levels-of-participants}}

As suggested by Rule 7, a significant challenge to presenting at Code
Club is selecting topics and activities that appeal to a critical mass
of the participants. This is particularly difficult if participants have
a wide range of coding experience, such as follows a turnover in group
membership. In these circumstances it can be useful to cover commonly
used tools but that might result in disinterest of more experienced
participants. We have identified several strategies to overcome the
challenges presented by participants at varying skill levels. Instead of
letting participants form their own pairs, the presenter can select
pairs of participants with either similar or differing skill levels,
depending on their goals. Partnerships between those with similar skill
levels requires the presenter to design appropriate activities each
skill level. We have found that commenting code is a good skill for
beginners since it forces them to dissect and understand a code chunk
line-by-line. An advantage of partnerships with disparate skill levels
is assigning a single task, which provides the presenter with a diverse
range of methods that achieve the same result. This approach to pairing
also helps to graft new members into the group that have emerging
programming skills. Regardless of how partners are selected, consider
asking the pairs to identify a navigator and a driver {[}5{]}. The
driver types at the computer while the navigator tells them what to
type, thus ensuring participation of both partners. Midway through the
activity, the presenter can have the partners switch roles.
Intentionally forming pairs can also engineer group interactions by
breaking up cliques, avoiding potentially disruptive partnerships, or
pairing reliable role models with new group members.

\hypertarget{rule-9-prepare-in-advance-to-maximize-participation}{%
\subsection{Rule 9: Prepare in advance to maximize
participation}\label{rule-9-prepare-in-advance-to-maximize-participation}}

It is not possible to fully participate in a Journal Club discussion
about a paper that the participant has not read. In that context, coming
to Code Club without having installed a dependency is similar to asking
a simple question about the Journal Club paper. Both instances show a
lack of respect and preparation. Just as a presenter must follow Rule 6
to provide materials ahead of time, participants must review the code in
advance, download the data sets, install the necessary packages, and
perhaps read up on the topic. If the Code Club is based on a paper or
chapters in a data science book (e.g., {[}6--8{]}), the participants
should read them before the session and consider how they might
incorporate the concepts into their own work.

\hypertarget{rule-10-participate}{%
\subsection{Rule 10: Participate}\label{rule-10-participate}}

An essential ingredient of any Code Club is active participation from
all parties. Having an open laptop on the table and permission to use it
can feel like an invitation to get distracted by other work, emails, and
browsing the internet; fight that urge and focus on the presenter's
goals. Be respectful and allow your partner to contribute. Speak up for
yourself and force your partner to let you contribute. If the material
seems too advanced for you, it can be frustrating, and tempting to
mentally check out. Fortunately, programming languages like R and Python
are generally expressive, which should allow you to engage with the
logic, even if the syntax is too advanced. Frankly, understanding the
logic of \emph{when} to use one modeling approach over another is more
important than knowing \emph{how} to use it. If you understand the
``why'', the ``how'' will quickly follow. More experienced participants
should aim to communicate feedback and coding suggestions at a level
that all participants can understand and engage in. Regardless of skill
levels, your partner and the presenter put themselves in a vulnerable
position by revealing what they do or do not know. Encourage them, and
show your gratitude for helping you learn something new, by fully
participating in each Code Club.

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

@@

\hypertarget{acknowledgements}{%
\subsection{Acknowledgements}\label{acknowledgements}}

All co-authors have been participants in the Code Clubs run as part of
PDS's lab meetings. They have had a critical role in shaping the
evolution of the sessions. AKH led a lab discussion of Code Clubs to
identify the key concepts presented, which were supplemented by
contributions from NL. The order of other co-authors is listed
alphabetically.

@@

\hypertarget{references}{%
\subsection{References}\label{references}}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Lonsdale2016}{}%
1. Lonsdale A, Penington JS, Rice T, Walker M, Dashnow H. Ten simple
rules for a bioinformatics journal club. Lewitter F, editor. PLOS
Computational Biology. 2016;12: e1004526.
doi:\href{https://doi.org/10.1371/journal.pcbi.1004526}{10.1371/journal.pcbi.1004526}

\leavevmode\hypertarget{ref-Wilson2014}{}%
2. Wilson G, Aruliah DA, Brown CT, Hong NPC, Davis M, Guy RT, et al.
Best practices for scientific computing. Eisen JA, editor. PLoS Biology.
2014;12: e1001745.
doi:\href{https://doi.org/10.1371/journal.pbio.1001745}{10.1371/journal.pbio.1001745}

\leavevmode\hypertarget{ref-Kothiyal2014}{}%
3. Kothiyal A, Murthy S, Iyer S. Think-pair-share in a large CS1 class.
Proceedings of the 2014 conference on innovation \& technology in
computer science education - ITiCSE 14. ACM Press; 2014.
doi:\href{https://doi.org/10.1145/2591708.2591739}{10.1145/2591708.2591739}

\leavevmode\hypertarget{ref-StackOverflow_MREE}{}%
4. Stack Overflow. How to create a minimal, reproducible example. 2020.
Available:
\url{https://stackoverflow.com/help/minimal-reproducible-example}

\leavevmode\hypertarget{ref-Bockeler_2020}{}%
5. Böckeler B, Siessegger N. On pair programming. 2020. Available:
\url{https://martinfowler.com/articles/on-pair-programming.html}

\leavevmode\hypertarget{ref-Wickham_2016}{}%
6. Wickham H, Grolemund G. O'Reilly Media; 2016. Available:
\url{https://r4ds.had.co.nz}

\leavevmode\hypertarget{ref-Schloss_2018}{}%
7. Schloss PD. The riffomonas reproducible research tutorial series.
Journal of Open Source Education. 2018;1: 13.
doi:\href{https://doi.org/10.21105/jose.00013}{10.21105/jose.00013}

\leavevmode\hypertarget{ref-Noble2009}{}%
8. Noble WS. A quick guide to organizing computational biology projects.
Lewitter F, editor. PLoS Computational Biology. 2009;5: e1000424.
doi:\href{https://doi.org/10.1371/journal.pcbi.1000424}{10.1371/journal.pcbi.1000424}

@@

\begin{longtable}[]{@{}ll@{}}
\toprule
\begin{minipage}[b]{0.25\columnwidth}\raggedright
\textbf{Title}\strut
\end{minipage} & \begin{minipage}[b]{0.69\columnwidth}\raggedright
\textbf{Description}\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.25\columnwidth}\raggedright
base vs.~ggplot\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Given input data and a figure, recreate the figure using R's base
graphics or ggplot syntax\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
Snakemake\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Given a bash script that contains an analysis pipeline, convert it to a
Snakemake workflow (can also be done with GNU Make)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
DRYing code\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Given script with repeated code, create functions to remove
repetition\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
mothur and Vegan\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Given a pairwise community dissimilarity matrix, compare communities
using the \texttt{adonis} function in the Vegan R package\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
tidy data\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Given a wide-formatted data table, convert it to a long, tidy-formatted
data table using tools from R's tidyverse\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
GitFlow\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Participants file and claim an issue to add their name to a README file
in a GitHub-hosted repository and file a pull request to complete the
issue\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
R with Google docs\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Scrape a Google docs workbook and clean the data to identify previous
Code Club presenters\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.25\columnwidth}\raggedright
Develop an R Package\strut
\end{minipage} & \begin{minipage}[t]{0.69\columnwidth}\raggedright
Convert a lab member's collection of scripts into package over a series
of sessions\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}
